CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-15 paper/ms.tex
Bug fixed

Working on it...

@@

Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars. The labels we use are from the Cannon, which means they are inferred labels.

@@

\bigskip
Now choose some examples from the 614 stars and make some plots.

@@

For spectrum with $a>c$, the optimized spectrum moves right a little bit, which means the real spectrum should move left a little. It's similar for $c>a$

@@

\bigskip
We also plot $Teff$ against log g. The color bar shows the mean inverse variance of these stars.

>>>>

Working on it...
I think one possible way is to use the velocities correction for the APOGEE data obtained from the spectrum calibration section. Then the optimized APOGEE spectrum can be represented as:
You should look into the velocities and find a right way to describe them.

@@

Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars. The labels we use in the figures are from the Cannon, which means they are inferred labels.

@@

\bigskip
Now choose some examples from the 614 stars and make some plots.Sometimes the inferred spectrum doesn't look like the data, which is already described in Ness et al 2015. We don't use these stars in the plots.

@@

For spectrum with $a>c$, the optimized spectrum moves left a little bit, which means the real spectrum should move right a little. It's similar for $c>a$. The c>a branch is not as obvious as the a>c branch.

@@

\bigskip
We also plot the inferred labels $Teff$ against log g. The color bar shows the mean inverse variance of these stars.
